### 2019-10-30 thesis/txt/5-study.tex
some additional graphics and graphics cleanups

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWSpdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWSpdf}
		\caption{Precision of Extractions per Number of Examples for SKWS}
		\label{fig:precision-skws}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWSpdf}
		\caption{Precision of SKWS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
		\caption{Precision of Extractions per Number of Examples for SKWS}
		\label{fig:precision-skws}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
		\caption{Precision of SKWS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
